\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-06 manuscript.Rmd
edited 2 references

Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [CITE REDCAP HERE 1, 2] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>). Participants for the anonymous online survey were recruited via the website of a Comic co-released with the survey [CITE COMIC HERE; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].

@@

To develop a shorter form of the LEBA we sought to Item response theory.IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017]. Here, an item’s quality is judged based on item information in relation to participants’ latent trait level ($\theta$). We gathered evidence on item quality  by fitting  each factor of LEBA with the graded response model to the combined EFA sample and CFA sample (n =690)(\@ref(tab:IRTparameters). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA. @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70. Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating  a good range of discrimination along the latent trait. Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.

>>>>

Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>). Participants were recruited via the website of a Comic co-released with the survey [CITE COMIC HERE; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].

@@

To develop a shorter form of the LEBA we sought to Item response theory.IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017]. Here, an item's quality is judged based on item information in relation to participants' latent trait level ($\theta$). We gathered evidence on item quality by fitting each factor of LEBA with the graded response model to the combined EFA sample and CFA sample (n =690)(\@ref(tab:IRTparameters). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA. @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70. Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait. Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.
